Neural Power Unit \\-- A Bayesian Approach To Neural Arithmetic

### 2020-05-22 papers/main.tex
simple function table

\todo{should this be here already?}
With the simple exemplary task of learning a function $f:\mathbb R^2 \rightarrow \mathbb R^2$
\begin{equation}
  \label{eq:xx_xdivy}
  f(\bm x) = f(x,y) = [xy,x/y] = \bm t
\end{equation}
we can demonstrate the strengths and weaknesses of the NALU.  The NALU only
learns successfully if it is trained on positive numbers, so we train with
samples from $\bm x \in \mathcal U^2(0.1,2)$ and plot the error $\epsilon =
|\bm t - \hat{\bm t}|^2$ in Fig.~\ref{fig:compare_npu_nmu_nalu_xy_xdivy}.

@@

The combination of NAU and NMU can thus learn $\{+,-,\times\}$, but no division.
This is shown in Fig.~\ref{fig:compare_npu_nmu_nalu_xy_xdivy} as well. The NMU
can perfectly represent the multiplication of the two inputs, but fails at
learning division.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{compare-npu-nmu-nalu-xy-xdivy.png}
  \caption{Comparison of different models learning the function
  $(x,y)\rightarrow(xy,x/y)$ with $(x,y)\in\mathcal U^2(0.1,2)$.  Each
  plot shows the mean-squared error on a logarithmic color scale ($\hat{\bm
  t}=\text{model}(\bm x)$).  The Dense network learns both multiplication and
  division, but fails to extrapolate. NALU learns both tasks perfectly, but
  completely fails if one of the inputs is negative.  The NMU successfully
  learns multiplication, but not division. Only the NPU learns both tasks and
  can extrapolate with an error that is less than $0.01$ in most places.}%
  \label{fig:compare_npu_nmu_nalu_xy_xdivy}
\end{figure}
\todo{add in depth experiment desc. of fig.~\ref{fig:compare_npu_nmu_nalu_xy_xdivy} in appendix}

@@

\appendix
\section*{Appendix A}%
\label{sec:appendix_a}

\todo{add sqrt to table~\ref{tab:compare_npu_npu_nalu}?}
\begin{table}[h]
  \centering
  \caption{Comparison of different $2\times2$ layers on the task
  $(x,y)\rightarrow(xy,\frac{x}{y})$.  $(x,y) \in \mathcal U^2(-2,2)$.}
  \label{tab:compare_npu_npu_nalu}
  \input{table-xy-xdivy-pos.tex}
\end{table}

>>>>

\todo{should this be here already?}
With the simple exemplary task of learning a function $f:\mathbb R^2 \rightarrow \mathbb R^2$
\begin{equation}
  \label{eq:xx_xdivy}
  f(\bm x) = f(x,y) = [xy,x/y] = \bm t
\end{equation}
we can demonstrate the strengths and weaknesses of the NALU.  The NALU only
learns successfully if it is trained on positive numbers, so we train with
samples from $\bm x \in \mathcal U^2(0.1,2)$ and plot the error $\epsilon =
|\bm t - \hat{\bm t}|^2$ in Fig.~\ref{fig:simple_err}.

@@

The combination of NAU and NMU can thus learn $\{+,-,\times\}$, but no division.
This is shown in Fig.~\ref{fig:simple_err} as well. The NMU
can perfectly represent the multiplication of the two inputs, but fails at
learning division.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.245\linewidth]{simple_err_add.pdf}
  \includegraphics[width=0.245\linewidth]{simple_err_mult.pdf}
  \includegraphics[width=0.245\linewidth]{simple_err_div.pdf}
  \includegraphics[width=0.245\linewidth]{simple_err_sqrt.pdf}
  \caption{Comparison of different models learning the function
  $(x,y)\rightarrow(xy,x/y)$ with $(x,y)\in\mathcal U^2(0.1,2)$.  Each
  plot shows the mean-squared error on a logarithmic color scale ($\hat{\bm
  t}=\text{model}(\bm x)$).  The Dense network learns both multiplication and
  division, but fails to extrapolate. NALU learns both tasks perfectly, but
  completely fails if one of the inputs is negative.  The NMU successfully
  learns multiplication, but not division. Only the NPU learns both tasks and
  can extrapolate with an error that is less than $0.01$ in most places.}%
  \label{fig:simple_err}
\end{figure}
\todo{add in depth experiment desc. of fig.~\ref{fig:simple_err} in appendix}
\begin{table}
  \centering
  \caption{Comparison of different $2\times2$ layers on the task
  $(x,y)\rightarrow(xy,\frac{x}{y})$.  $(x,y) \in \mathcal U^2(-2,2)$.}
  \label{tab:simple_err}
  \input{simple_err.tex}
\end{table}

@@
